---
title: "Draft Visualizationa for Semester Project"
output: html_document
---
#Loading the Data and Necessary Packages
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
#Insert the location of your data here, for example
health <- read.csv("mentalsurvey_clean.csv")
```

#Section 1: Showing that Mental and Behavioral Health Issues Impact Workers

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Section 2: What are Other Companies Doing to Assist workers with Mental and Behavioral Health Policies

```{r}

```

#Section 3: What are Factors that Might Limit the Impact of Behavioral Health Outreach

##Anonymity Policies 

If employees feel that their anonymity is not protected, they may be less likely to reach out for help.

###Anonymity Policies by Company Size

####Crosstab Table

```{r}
#Put company size in order
CompanySize  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
#Create Cross-tab Table
APbCS <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., CompanySize)
head(APbCS)
```

####Proportions table

```{r}
#Create a proportions table by Row
prop.table(APbCS, 2)
```

####Chi-Squared Test 

```{r}
#Do a chi-squared test
chisq.test(APbCS)
```

####Visualization of Data

```{r}
ggplot(health, aes(CompanySize, health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)) + geom_jitter(height = .3, width = .3) + ggtitle("Anonymity Protections For Mental Health Services") + xlab("Company Size") + ylab("Is Anonymity Protected?") 
```

####Interpretation of Results 

The table and chart above show that across all company sizes, most respondents indicate that they do not know what their current company's anonymity policy is towards those using mental health services.  For companies of 1-5 employees, the next most common answer is "No" (anonymity is not protected). However, for companies larger than 5 employees, the results appear fairly consistent, with the majority of respondents (60-70 percent) indicating that they do not know anonymity policies, a sizable minority of respondents saying that anonymity is protected (25-32 percent), and less than 10 percent of respondents in each group saying anonymity is not protected. Based off of the chi-squared test, it is not clear if there is a statistically significant difference in anonymity policies of companies of different sizes.  

###Anonymity Policies by Whether it is a Tech Company

####Cross-tab Table

```{r}
#Add labels to tech company org
TLabel <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
levels = c(0, 1),
labels = c("No", "Yes"))
#Create a crosstab table
APbT2 <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., TLabel)
head(APbT2)
```

####Proportions table

```{r}
#Create a proportions table by Row
prop.table(APbT2, 2)
```

####Chi-Squared Test 

```{r}
#Do a chi-squared test
chisq.test(APbT2)
```

####Visualization of Data

OPTION 1

```{r}
ggplot(health, aes(TLabel, health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)) + geom_jitter(height = .3, width = .3) + ggtitle("Anonymity Protections For Tech vs. Non-Tech Companies") + xlab("Is Employer Primarily Tech?") + ylab("Is Anonymity Protected?") 
```

OPTION 2

```{r}
#Run Counts
summary(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)
#Modify Labels
levels(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.) <- c("Don't Know Anonymity Policy", "Anonymity Not Protected", "Anonymity Protected")
#Check to make sure
summary(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)
```

```{r}
#Create Visualization
p3 <- ggplot(health, aes(x = TLabel))+geom_bar()+facet_wrap(~ health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.)+ ggtitle("Anonymity Protections For Tech vs. Non-Tech Companies") + xlab("Is Employer Primarily Tech?") + ylab("Count") 
p3
```

####Interpretation of Results 

The difference between primarily tech and non-primarily tech companies is not statistically significant in regards to anonymity policies for those seeking mental health services.  In both cases, the clear majority of those surveyed indicated that they do not know  their current company's anonymity policy is towards those using mental health services.  In both cases, the next most common response to the question is that anonymity is protected for those using mental health services.

##Ease of Asking for Leave For A Mental Health Issue

This is important because if employees feel that asking for time off from work for medical leave, they may be less likely to seek the help they need. 

###Answers by Gender

```{r}
#Crosstab table
ELDbG <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$gender)
ELDbG
```

####Chi-Squared 

We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.  However, it potentially indicates that that the differences between genders may not be statistically significant (or we do not have enough information)

```{r}
chisq.test(ELDbG)
```


###Answers by Age Group

```{r}
#Do the AgeGroup Variable
labs <- c(paste(seq(17, 74, by = 20), seq(37, 80, by = 20),
                sep = "-"))
health$AgeGroup <- cut(health$age, breaks = c(seq(17, 74, by = 20), Inf), labels = labs, right = FALSE)
```

```{r}
#Crosstab table
ELDbA <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$AgeGroup)
ELDbA
```

We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.  However, it potentially indicates that that the differences between age groups may not be statistically significant (or we do not have enough information)

###Chi-Squared
```{r}
chisq.test(ELDbA)
```


###Answers by Company Size

```{r}
#Crosstab table
ELDbCS <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., ENumOrder)
ELDbCS
```

###Chi-Squared

```{r}
chisq.test(ELDbCS)
```


###Answers by Whether Company is Primarily a Tech Company

```{r}

```

####Chi-Squared

```{r}

```

###Answers by Whether Anonymity Is Protected

```{r}

```

####Chi-Squared

```{r}

```

###Answers by Whether Current Company Provides Mental Health Benefits

```{r}
#Crosstab Table
ELDbMHB <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
ELDbMHB
```

###Chi-Squared

```{r}
chisq.test(ELDbMHB)
```

###Answers by Whether Current Company Has Ever Formally Discussed Mental Health

```{r}
ELDbEDM <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
ELDbEDM
```

####Chi-Squared

```{r}
chisq.test(ELDbEDM)
```

###Answers by Whether Current Company Offers Other Resources

```{r}
ELDbEOR <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
ELDbEOR
```

####Chi-Squared 

```{r}
chisq.test(ELDbEOR)
```

###Answers by If They Ever Saw A Poor Response to Mental Health Issue

```{r}
ELDbPR <- table(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
ELDbPR
```

####Chi-Squared
```{r}
chisq.test(ELDbPR)
```

##Comfort with talking to Supervisor About Mental Health

This is important because if an employee has a mental health issue, they should ideally be comfortable discussing it with a supervisor in case they need additional assistance. In addition, we may want to consider training supervisors on how to handle instances where employees reach out to them about mental health. 

###Answers by Gender

```{r}
MHbG <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$gender)
MHbG
```

####Chi-Squared

```{r}
chisq.test(MHbG)
```

###Answers by Age Group

```{r}
MHbA <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$AgeGroup)
MHbA
```

####Chi-Squared

```{r}
chisq.test(MHbA)
```

###Answers by Company Size
```{r}
MHbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., ENumOrder)
MHbCS
```

####Chi-Squared
```{r}
chisq.test(MHbCS)
```

###Answers by Whether Company is Primarily a Tech Company

```{r}

```

###Answers by Whether Anonymity Is Protected

```{r}

```

###Answers by Whether Current Company Provides Mental Health Benefits

```{r}
MHbMHB <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
MHbMHB
```

####Chi-Squared
```{r}
chisq.test(MHbMHB)
```


###Answers by Whether Current Company Has Ever Formally Discussed Mental Health

```{r}
MHbEDM <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
MHbEDM
```

####Chi-Squared

```{r}
chisq.test(MHbEDM)
```

###Answers by Whether Current Company Offers Other Resources

```{r}
MHbEOR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
MHbEOR
```

####Chi-Squared

```{r}
chisq.test(MHbEOR)
```

###Answers by If They Ever Saw A Poor Response to Mental Health Issue

```{r}
MHbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
MHbPR
```

####Chi-Squared

```{r}
chisq.test(MHbPR)
```

###Answers by If They Think Supervisor Would View Them Negatively If They Knew You Suffered From a Mental Health Issue

```{r}

```

##Comfort with taking to Coworkers About Mental Health

This is important because if an employee has a mental health issue, they should ideally be comfortable discussing it with a coworkers in case they need additional assistance. In addition, we may want to consider training employees on how to handle instances where coworkers reach out to them about mental health. 

###Answers by Gender

```{r}
MHCbG <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$gender)
MHCbG
```

####Chi-Squared

```{r}
chisq.test(MHCbG)
```

###Answers by Age Group

```{r}
MHCbA <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$AgeGroup)
MHCbA
#Proportions (as column percentages)
prop.table(MHCbA, 2)
#Chi-Squared (We get a big chi-quared and a warning it may be incorrect, likely b/c small values for the 57-77 column)
chisq.test(MHCbA)
```

###Answers by Company Size

```{r}
MHCbCS <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., ENumOrder)
MHCbCS
#Proportions (as column percentages)
prop.table(MHCbCS, 2)
#Chi-Squared (the p value is small)
chisq.test(MHCbCS)
```

###Answers by Whether Company is Primarily a Tech Company

```{r}

```

###Answers by Whether Anonymity Is Protected

```{r}

```

###Answers by Whether Current Company Provides Mental Health Benefits

```{r}
MHCbMHB <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.)
MHCbMHB
```

####Chi-Squared

```{r}
chisq.test(MHCbMHB)
```

###Answers by Whether Current Company Has Ever Formally Discussed Mental Health

```{r}
MHCbEDM <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
MHCbEDM
```

####Chi-Squared
```{r}
chisq.test(MHCbEDM)
```

###Answers by Whether Current Company Offers Other Resources

```{r}
MHCbEOR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
MHCbEOR
```

####Chi-Squared

```{r}
chisq.test(MHCbEOR)
```

###Answers by If They Ever Saw A Poor Response to Mental Health Issue

```{r}
MHCbPR <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
MHCbPR
```

####Chi-Squared

```{r}
chisq.test(MHCbPR)
```

###Answers by If They Think Coworkers Would View Them Negatively If They Knew You Suffered From a Mental Health Issue

```{r}
MHCbCN <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.coworkers., health$Do.you.think.that.team.members.co.workers.would.view.you.more.negatively.if.they.knew.you.suffered.from.a.mental.health.issue.)
MHCbCN
```

####Chi-Squared
```{r}
chisq.test(MHCbCN)
```

